Taking Linear Logic Apart

### 2018-04-06 doc/tlla2018/main.tex
Removed PDF; fixed .travis.yml; added theorems to main.tex

\documentclass[submission,copyright,creativecommons]{eptcs}
\providecommand{\event}{Linearity and TLLA 2018} % Name of the event you are submitting to
\usepackage{breakurl} % Not needed if you use pdflatex only.
\usepackage{underscore} % Only needed if you use pdflatex.
\usepackage{textcomp,textgreek,upgreek} % Minimal dependencies for bibTeX.
\usepackage{amsthm}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\input{preamble-typing}
\renewcommand*{\hccp}{HTA\xspace}

@@

\begin{theorem}\label{thm:cp2hcp-typing}
  If $\seq[P]{\Gamma}$ in \cp, then $\seq[P]{\Gamma}$ in \hcp.
\end{theorem}
\begin{theorem}\label{thm:hcp2cp-typing}
  If $\seq[P]{\Gamma}$ in \hcp, then $\seq[P]{\Gamma}$ in \cp.
\end{theorem}
\begin{definition}\label{def:hcp-bigtens}
  \(\!%
  \begin{array}{lcl}
    \ty{\bigparr\emptycontext}
    & = & \ty{\bot}
    \\
    \ty{\bigparr(\tmty{x_1}{A_1}, \dots, \tmty{x_n}{A_n})}
    & = & \ty{A_1 \parr \dots \parr A_n}
  \end{array}
  \)
\end{definition}
\begin{lemma}\label{lem:hcp-bigparr}
  If $\seq{\Gamma}$ in \hcp, then $\seq{\bigparr\Gamma}$ in \hcp.
\end{lemma}
\begin{definition}\label{def:hcp-bigtens}
  \(\!%
  \begin{array}{lcl}
    \ty{\bigtens\emptyhypercontext}
    & = & \ty{\one}
    \\
    \ty{\bigtens(\Gamma_1 \hsep \dots \hsep \Gamma_n)}
    & = & \ty{\bigparr\Gamma_1 \tens \dots \tens \bigparr\Gamma_n}
  \end{array}
  \)
\end{definition}
\begin{theorem}\label{thm:hcp-bigtens}
  If $\seq{\mathcal{G}}$ in \hcp, then $\seq{\bigtens\mathcal{G}}$ in \hcp.
\end{theorem}
\begin{corollary}[Conservative Extension]
  If $\seq{\mathcal{G}}$ in \hcp, then $\seq{\bigtens\mathcal{G}}$ in \cp.
\end{corollary}

@@

\begin{theorem}\label{thm:hcp2hccp-typing}
  If $\seq[P]{\mathcal{G}}$ in \hcp, then $\seq[P]{\mathcal{G}}$ in \hccp.
\end{theorem}
\begin{theorem}\label{thm:hccp2hcp-typing}
  If $\seq{\mathcal{G}}$ in \hccp, then $\seq{\mathcal{G}}$ in \hcp.
\end{theorem}

>>>>

\documentclass[submission,copyright,creativecommons]{eptcs}
\providecommand{\event}{Linearity and TLLA 2018} % Name of the event you are submitting to
\usepackage{breakurl} % Not needed if you use pdflatex only.
\usepackage{underscore} % Only needed if you use pdflatex.
\usepackage{textcomp,textgreek,upgreek} % Minimal dependencies for bibTeX.
\usepackage{amsthm}
\newtheorem{definition}{Definition}
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{corollary}{Corollary}
\input{preamble-typing}

@@

\begin{theorem}\label{thm:cp2hcp-typing}
  If $\seq[P]{\Gamma}$ in \cp, then $\seq[P]{\Gamma}$ in \hcp.
\end{theorem}
\begin{theorem}\label{thm:hcp2cp-typing}
  If $\seq[P]{\Gamma}$ in \hcp, then $\seq[P]{\Gamma}$ in \cp.
\end{theorem}
\begin{definition}\label{def:hcp-bigtens}
  \(\!%
  \begin{array}{lcl}
    \ty{\bigparr\emptycontext}
    & = & \ty{\bot}
    \\
    \ty{\bigparr(\tmty{x_1}{A_1}, \dots, \tmty{x_n}{A_n})}
    & = & \ty{A_1 \parr \dots \parr A_n}
  \end{array}
  \)
\end{definition}
\begin{lemma}\label{lem:hcp-bigparr}
  If $\seq{\Gamma}$ in \hcp, then $\seq{\bigparr\Gamma}$ in \hcp.
\end{lemma}
\begin{definition}\label{def:hcp-bigtens}
  \(\!%
  \begin{array}{lcl}
    \ty{\bigtens\emptyhypercontext}
    & = & \ty{\one}
    \\
    \ty{\bigtens(\Gamma_1 \hsep \dots \hsep \Gamma_n)}
    & = & \ty{\bigparr\Gamma_1 \tens \dots \tens \bigparr\Gamma_n}
  \end{array}
  \)
\end{definition}
\begin{theorem}\label{thm:hcp-bigtens}
  If $\seq{\mathcal{G}}$ in \hcp, then $\seq{\bigtens\mathcal{G}}$ in \hcp.
\end{theorem}
\begin{corollary}\label{cor:hcp-bigtens}
  If $\seq{\mathcal{G}}$ in \hcp, then $\seq{\bigtens\mathcal{G}}$ in \cp.
\end{corollary}

@@

\begin{theorem}\label{cor:hcp2hccp-typing}
  If $\seq[P]{\mathcal{G}}$ in \hcp, then $\seq[P]{\mathcal{G}}$ in \hccp.
\end{theorem}
\begin{corollary}\label{thm:cp2hccp-typing}
  If $\seq[P]{\Gamma}$ in \cp, then $\seq[P]{\Gamma}$ in \hccp. 
\end{corollary}
\begin{theorem}\label{thm:hccp2hcp-typing}
  If $\seq{\mathcal{G}}$ in \hccp, then $\seq{\mathcal{G}}$ in \hcp.
\end{theorem}
\begin{corollary}\label{cor:hccp2cp-typing}
  If $\seq{\mathcal{G}}$ in \hccp, then $\seq{\bigtens\mathcal{G}}$ in \cp.
\end{corollary}
